maASlin2

### 2019-12-19 scripts/27_maASlin2.Rmd
update

```{r}
# remove everything already in this folder
#system('rm ../data/maASlin2/pw/*')

fit_data <- Maaslin2(
    pw, pheno_final, '../data/maASlin2/pw/onlyFixed', 
    normalization  = 'NONE', 
    transform = "LOG",  
    cores = 4, 
    plot_heatmap = F,
    min_abundance = 0.05,
    min_prevalence = 0.1,
    fixed_effects = c('Toxicity', 
                      'CR',
                      'Disease_Class',
                      'disease_sta',
                      'abx_expo', 
                      'ferritin',
                      'crp',
                      'IL_1_beta',
                      #'IL_10',
                      'IL_6',
                      'Prior_lines_of_therapy',
                      'Antibiotics_4_weeks_post_CAR_T_cells'),
    # random_effects = c('sex',
    #                   'age'),
    standardize = FALSE,
    max_significance = 0.25)

@@

fit_data <- Maaslin2(
    pw, pheno_final, '../data/maASlin2/pw/both', 
    normalization  = 'NONE', 
    transform = "LOG",  
    cores = 4, 
    plot_heatmap = F,
    min_abundance = 0.05,
    min_prevalence = 0.1,
    fixed_effects = c('Toxicity', 
                      'CR',
                      'Disease_Class',
                      'disease_sta',
                      'abx_expo', 
                      'ferritin',
                      'crp',
                      #'IL_1_beta',
                      #'IL_10',
                      #'IL_6',
                      'Prior_lines_of_therapy',
                      'Antibiotics_4_weeks_post_CAR_T_cells'),
    random_effects = c('sex',
                      'age'),
    standardize = FALSE,
    max_significance = 0.25)
```

>>>>

```{r}
# remove everything already in this folder
system('rm ../data/maASlin2/pw/onlyFixed/*')

fit_data <- Maaslin2(
    pw, pheno_final, '../data/maASlin2/pw/onlyFixed', 
    normalization  = 'NONE', 
    transform = "LOG",  
    cores = 4, 
    plot_heatmap = F,
    min_abundance = 0.05,
    min_prevalence = 0.1,
    fixed_effects = c('Toxicity', 
                      'CR',
                      'Disease_Class',
                      'disease_sta',
                      'abx_expo', 
                      'ferritin',
                      'crp',
                      'IL_1_beta',
                      #'IL_10',
                      'IL_6',
                      'Prior_lines_of_therapy',
                      'sex',
                      'age',
                      'Antibiotics_4_weeks_post_CAR_T_cells'),
    standardize = FALSE,
    max_significance = 0.25)

@@

fit_data <- Maaslin2(
    pw, pheno_final, '../data/maASlin2/pw/both', 
    normalization  = 'NONE', 
    transform = "LOG",  
    cores = 4, 
    plot_heatmap = F,
    min_abundance = 0.05,
    min_prevalence = 0.1,
    fixed_effects = c('Toxicity', 
                      'CR',
                      'Disease_Class',
                      'disease_sta',
                      'abx_expo', 
                      'ferritin',
                      'crp',
                      'IL_1_beta',
                      #'IL_10',
                      'IL_6',
                      'Prior_lines_of_therapy',
                      'Antibiotics_4_weeks_post_CAR_T_cells'),
    random_effects = c('sex',
                      'age'),
    standardize = FALSE,
    max_significance = 0.25)
```
